Magnetized accretion disks around Kerr black holes with scalar hair

### 2017-11-28 kbhssh_disks/paper_prd.tex
PRD_version

\documentclass{aa}  
\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{hyperref}
\usepackage{color}
\usepackage{float}

@@

@@

%   \subtitle{}

\author{Sergio Gimeno-Soler\inst{1}, Jos\'e A.~Font\inst{1,2}, Carlos Herdeiro \inst{3}, Eugen Radu\inst{3}}
\institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\\email{sergio.gimeno@uv.es}
\and
Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico Jos\'e Beltr\'an 2, 46980, Paterna (Val\`encia), Spain. \\
\email{j.antonio.font@uv.es}
\and
Departamento de F\'isica da Universidade de Aveiro and Centre for Research and Development in Mathematics and Applications (CIDMA), Campus de Santiago, 3810-183 Aveiro, Portugal
}

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory

  \date{}

  \abstract
  {We present a method to build magnetized constant angular momentum disks around Kerr black holes with scalar hair (KBHsSH).}

   \keywords{black hole physics
               }

   \maketitle
%
%-------------------------------------------------------------------

@@

% Outline:

% Brief description of the work of Herdeiro, recall what we use here and proceed to describe what we have done.
% First, describe framework. Metric, energy-momentum tensor, and equations of motion. Second, angular momentum distribution (including the angular momentum at $r_{\mathrm{mb}}$) and EoS. Third, results: Higher potential well than any possible Kerr-like solution with $r_{\mathrm{in}} = r_{\mathrm{mb}}$. We should graph here the potential well $\Delta W$ vs. the normalized spin parameter $a$ for the KBH case. Maybe get the data for intermediate values of magnetization? I think it is important to have more data of HBH, to test some ideas. Comparison with naked singularities? I would like to obtain the rest-mass and gravitational mass of the total distribution (torus + scalar field).

% Comparison of the structure of the disks obtained for the case of KBHsSH with KBH and Naked Singularities (NS). $\Delta W$, angular velocity, angular momentum, mass of the torus and physical magnitudes (thermodynamical)

% Paint same curves (if possible) as in the case of the previous paper for magnetized toris around KBHs, check differences between the cases. For KBHs with full-relativistic fluid and HBHs.

% Check relations between ergoregions in KBHs and NSs spacetimes and KBHsSH case (morphology?)
% The most important conclusion is we obtain very different disk configurations for HBHs and for KBHs (with the same ADM or Horizon quantities), therefore we can asymptotically distinguish a disk around a KBHsSH from a disk around a KBH. (potential well and so on).

%--------------------------------------------------------------------
\section{Framework}

@@

\bibliographystyle{bibtex/aa}
\bibliography{references}

>>>>

%-----------------------------------------------------------------------
%
% filename = nube.tex
%
% First version: February 2012
% Last revision: April 2012
%
%-----------------------------------------------------------------------

\documentclass[aps, prl, amsmath, floats,floatfix, twocolumn, superscriptaddress, nofootinbib, 
showpacs]{revtex4}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   LOAD PACKAGES   %%%
%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{color}
\usepackage{graphicx,subfigure}
\usepackage{units}
\usepackage{slashbox}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   BEGIN DOCUMENT  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%
%%%   MACROS   %%%
%%%%%%%%%%%%%%%%%%

\definecolor{orange}{rgb}{0.9,0.45,0}

\renewcommand{\t}{\times}

\long\def\symbolfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}

%%%%%%%%%%%%%%%%%
%%%   TITLE   %%%
%%%%%%%%%%%%%%%%%

@@

\author{Sergio Gimeno-Soler}
\affiliation{Departamento de
  Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia,
  Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}

\author{Jos\'e A. Font}
\affiliation{Departamento de
  Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia,
  Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}
\affiliation{Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico 
  Jos\'e Beltr\'an 2, 46980, Paterna (Val\`encia), Spain}

\author{Carlos Herdeiro}
\affiliation{Departamento de F\'{\i}sica da Universidade de Aveiro and CIDMA, Campus de Santiago, 
3810-183 Aveiro, Portugal}

\author{Eugen Radu}
\affiliation{Departamento de F\'{\i}sica da Universidade de Aveiro and CIDMA, Campus de Santiago, 
3810-183 Aveiro, Portugal}

%%%%%%%%%%%%%%%%
%%%   DATE   %%%
%%%%%%%%%%%%%%%%

\date{today}

%%%%%%%%%%%%%%%%%%%%
%%%   ABSTRACT   %%%
%%%%%%%%%%%%%%%%%%%%

\begin{abstract} 
We present a method to build magnetized constant angular momentum disks around Kerr black holes with scalar hair (KBHsSH).
\end{abstract}

%%%%%%%%%%%%%%%%
%%%   PACS   %%%
%%%%%%%%%%%%%%%%

\pacs{
95.30.Sf, % relativity and gravitation
04.70.Bw, 
04.40.Nr, 
04.25.dg
}

%%%%%%%%%%%%%%%%%%%%%%
%%%   MAKE TITLE   %%%
%%%%%%%%%%%%%%%%%%%%%%

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%
%%%   INTRODUCTION   %%%
%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{}

\section{Framework}

%%%%%%%%%%%%%%%%%%%%%
%%%   RESULTS   %%%
%%%%%%%%%%%%%%%%%%%%%

@@

\bibliographystyle{apsrev}
\bibliography{references}
